Investigating soundscapes perception through acoustic scenes simulation

### 2018-06-27 v2/responseToReviewers.tex

\section{Answer to Reviewer 1}

\begin{enumerate}

\item \emph{The utility of this tool beyond the experiments presented here is not apparent because the flexibility of the system was not demonstrated, for example:
- SimScene itself was only used in the first experiment, and other applications of it were not considered. Design choices vary widely between researchers and domains, meaning that the specific instantiations here may not be generally useful.}

$\rightarrow$ We definitely agree. As now discussed in more detail in Section 6 of the manuscript, the proposed software tool is not designed for genericity by we believe that the proposed specific design strategies and use of recent software toolkits can be considered as inspirations for desiging other experimental protocols questionning soundscape perception.

@@

\item \emph{In the last sentence of the abstract, the distinction of 'physical descriptors' vs. 'global descriptors'  does not have enough context here to be informative.}

$\rightarrow$ This sentence have be rewritten to be more explicit: "acoustic pressure levels computed for specific sound sources better characterize the appraisal than the acoustic pressure level computed over the overall soundscape."

\item \emph{In section 2.1 (pg. 5), the citations (particularly 27-31) do not seem relevant for justifying the event/texture distinction in the simulator.}

$\rightarrow$ The references to the ASA theory and statistical processing of textures are now removed. The work of Nelken and de Cheveigné is still cited as, in our humble opinion, it describes a soundscape model that is very close to the one used in the study described in this paper.

### 2018-06-28 lafaySimulatedScenePerception.tex
remove some acronyms

Finally, this work allows us to conjecture as to the nature of the mental representations of the concepts "pleasant (urban sound) environment" (PE) and "unpleasant (urban sound) environment" (UE).

@@

First, the fact that the semantic information (which sound source is present) and compositional information (at which level) are different for ideal and non-ideal scenes leads us to believe that these two types of information characterize the PE and UE concepts.

>>>>

Finally, this work allows us to conjecture as to the nature of the mental representations of the concepts "pleasant urban sound environment" and "unpleasant urban sound environment" .

@@

First, the fact that the semantic information (which sound source is present) and compositional information (at which level) are different for ideal and non-ideal scenes leads us to believe that these two types of information characterize the above cited concepts.
